smdi: An R package to perform structural missing data investigations on partially observed confounders in real-world evidence studies

### 2023-12-05 manuscript/manuscript.qmd
implemented wording suggested by RJD co-author review and adjusted worde count

[**Word count:**]{.underline} 2,514 words

@@

The package does come with certain limitations, such that the true underlying mechanism causing the missing data can never be inferred with absolute certainty from the observed data. Therefore, it's important to complement diagnostic results with substantive expert knowledge to factor in how covariates are measured in routine care and contextualize potential reasons for missingness. This collaborative approach allows for a contextualized understanding of potential causes for missing data in EHR.

>>>>

[**Word count:**]{.underline} 2,522 words

@@

The package should be used with certain limitations in mind. Most importantly, the true underlying mechanism causing the missing data can never be inferred with absolute certainty from the observed data. Therefore, it is important to complement diagnostic results with substantive expert knowledge to factor in how covariates are measured in routine care, which could be system-specific, and contextualize potential reasons for missingness. This collaborative approach allows for a contextualized understanding of potential causes for missing data in EHR.
